Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-18 paper.tex
chore: minor
reply to lukas

  \delta (|y - \hat{y}| - \frac{1}{2} \delta) & \text{otherwise,} 

@@

where $\delta$ is a hyperparameter that determines the threshold between the two loss functions and $y$ and $\hat{y}$ are the target and predicted values, respectively.

@@

\lukas{what is the value of $\delta$ in the training?}
\lukas{also: $\delta$ is used as a function and as a value?}

@@

Examples of all three types of experiment are shown in~\Cref{fig:scenarios}. %\lukas{can we create a figure with at least 3 sample scenarios (1 stationary, 2 split, 1 moving (with a line indicating its trajectory))?}

>>>>

  \delta \cdot (|y - \hat{y}| - \frac{1}{2} \delta) & \text{otherwise,} 

@@

where $\delta$ is a hyperparameter that determines the threshold between the two loss functions (fixed to 1 in our experiemnt) and $y$ and $\hat{y}$ are the target and predicted values, respectively.

@@

%\lukas{what is the value of $\delta$ in the training?}
%\lukas{also: $\delta$ is used as a function and as a value?}

@@

Examples of all three types of experiments are shown in~\Cref{fig:scenarios}. %\lukas{can we create a figure with at least 3 sample scenarios (1 stationary, 2 split, 1 moving (with a line indicating its trajectory))?}
